Fitbit & ET Glasses - Methods

### 2022-09-24 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/FitBit_ET_Glasses_Methods.Rmd
update R script fitbit filter

plot_flow <-
ggplot(data = df_heart_all,
       mapping = aes(x = as.numeric(Time),
                     y = `Heart Rate`,
                     group = ID)
       ) +
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            ) +
  xlim(0, min(df_heart_min$min)) +
  scale_color_viridis_d(option = "A",
                       end = 0.8)  +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.position = "none",
        strip.text = element_text(size = 16)) +
  facet_grid(cols = vars(Type),
             scales = "free_x")

@@

@@

>>>>

############### FLOW PLOT #############
plot_flow <-
ggplot(data = df_heart_all,
       mapping = aes(x = as.numeric(Time),
                     y = `Heart Rate`,
                     group = ID)
       ) +
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            ) +
  xlim(0, min(df_heart_min$min)) +
  scale_color_viridis_d(option = "A",
                       end = 0.8)  +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.position = "none",
        strip.text = element_text(size = 16)) +
  facet_grid(cols = vars(Type),
             scales = "free_x")

@@

############### LOESS PLOT #############

@@

############### BOX PLOT #############
